---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(rulsif.ts)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rulsif.ts

<!-- badges: start -->
<!-- badges: end -->

`rulsif.ts` implements relative unconstrained least squares importance fitting for the task
of detecting change points in time series data. The primary function is `ts_detect` which returns
a sequence of change point scores for each time point starting at a specified point in the series.

```{r, echo = F}
ts <- c(rnorm(100, 0, 0.5), rnorm(150, 5, 0.5), rnorm(75, -1, 0.5))
d <- ts_detect(ts, make_plot = TRUE)
```


## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("connorbrubaker/rulsif.ts")
```

## References

* Song Liu, et al. "Change-point detection in time-series data by relative density-ratio estimation".
  In: *Neural Networks* 43 (2013), pp. 72-83. ISSN: 0893-6080. DOI: `10.1016/j.neunet.2013.01.012.`

* Masashi, et al. "Direct importance estimation for covariance shift adaptation." In: *Annals of the Institute
of Statistical Mathematics* 60.4 (2008), pp. 699-746. ISSN: 0020-3157. DOI: `10.1007/s10463-008-0197-x.`
